
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute open ETCS}
\author{Hekele, Bernd}
\date{2013-02-15}

\begin{document}
\section*{\large{Meeting Minute open ETCS \ \ \ \ 2013-02-15}}

\large{\emph{Called up by: \ \  Dr. Klaus Ruediger Hase.}}

\subsection*{Participants:} WP4, Marc Behrens, Armand Nachef, CyrilCornu, Jan Welte, Jan Welvaarts,  Fausto Cocchetti, Marielle Petit-Doche, Merlin Pokam, Joao Santos, Rico Kaseroni, Uwe Steinke, Stefan Rieger\\

\subsection*{Meeting Time: from 10:00h \ to: \ 10:30h}

\subsection*{Type of conference: Telco}

\line(1,0){400}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Intermediate Report to DLR
\item Formal Tools Workshop
\item Going Public of Repositories
\end{enumerate}
\line(1,0){400}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Report is due today, i.e., Friday, 15th February.\newline
If report cannot be sent in time the delay has to be announced to Holger Stegemann (TO) and Yvonne Loehel (CC), both at dlr.de.\newline
Please, send a copy of the report (resp. the delay announcement) to project-office. The copy is also needed to prepare the German cluster summary report and the project report to ITEA. 
For ITEA reporting a English version of the report is highly appreciated.

\item Formal Tools workshop\newline
Regarding schedule the best match for most of the participants is week beginning 15th of April. In order to prepare a decision on which tool to select a Evaluation Matrix is proposed. It is planned to agree on this matrix during the workshop. We expect three dimensions in this matrix: aspect, rating, and weight. DB proposes to prepare a  starting version of this matrix. Another option is to call input via Wiki. Discussion has to be continued.

\item Going public of repositories\newline
The proposal to move a (here the toolchain) repository has been discussed. From WP7 only positive responses were reported. As a final procedure a formal "committer voting" was proposed.

\end{enumerate}

\line(1,0){400}
\section*{\underline{Notes}}

\end{document}
