
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute open ETCS}
\author{Hekele, Bernd}
\date{2013-03-06}

\begin{document}
\section*{\large{Meeting Minute open ETCS \ \ \ \ 2013-03-01}}

\large{\emph{Called up by: \ \  Dr. Klaus Ruediger Hase.}}

\subsection*{Participants:} WP4, Marc Behrens, Cyril Cornu, Jens Gerlach, Frank Golotkowski, Baseliyos Jacob, Marielle Petit-Doche, Merlin Pokam, Joao Santos, Uwe Steinke, Stefan Rieger, Jan Welte, Roberto, Kretschmer\\

\subsection*{Meeting Time: from 10:00h \ to: \ 10:30h}

\subsection*{Type of conference: Telco}

\line(1,0){400}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Macro Planning of WP4 tasks
\item Safety Strategy Workshop
\item Internal Assessor
\end{enumerate}
\line(1,0){400}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Macro Planning of WP4 tasks\newline

\item Safety Strategy Workshop\newline
Starting March 11th a sequence of two workshops is scheduled. The first is covering the topic "Requirements for API", the second is related to the Safety strategy. Intention of the organiser is to limit participation to a minimum. Topics for the workshops to be collected in planning meetings. 

\item New Task Internal Assessor\newline
The internal assessor is foreseen to act in the same way an external assessor would do. Activities to plan the internal assessor and make the internal assessor transparent are part of the new Internal Assessor task. Task is agreed to be started as a task in WP4. Cyril Cornu from All4Tech will take the lead. Other Work Packages activities are to be coordinated in this task.\newline
The interaction of using Scrum in the project and hard control of Cenelec is not sufficiently understood in the project. Scrum is widely in use in other security relevant areas, like automotive or defence. In order to raise transparency in the project and gain trust in the chosen approach a meeting will be scheduled to discuss the issue.

\end{enumerate}

\line(1,0){400}
\section*{\underline{Notes}}

\end{document}
