
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute open ETCS}
\author{Kaseroni, Rico}
\date{2013-03-08}

\begin{document}
\section*{\large{Meeting Minute open ETCS \ \ \ \ 2013-03-08}}

\large{\emph{Called up by: \ \  Dr. Klaus Ruediger Hase.}}

\subsection*{Participants:} QA Plan, Marc Behrens, Cyril Cornu,Rico Kaseroni,  Merlin Pokam,  Jan Welte, Bernd Hekele, Klaus-Ruediger Hase, Peter Mahlmann, \\

\subsection*{Meeting Time: from 09:00h \ to: \ 10:00h}

\subsection*{Type of conference: Telco}

\line(1,0){400}
\section*{\underline{Agenda}}
\begin{enumerate}
\item QA Plan elaboration 

\end{enumerate}
\line(1,0){400}
\section*{\underline{Discussion}}
We @Project office and some WP4 members had a Meeting on QA Plan
 development Today morning.
 
All members agreed that QA Plan needs further development and can not go
 under a formal review process right now.
 
We agreed that we have to add some more content on one side and at the same
 time we have to get rid of some other parts.
 
Two ideas went in general  under investigation :
\begin{enumerate}
 \item The QA Plan has to be the bible of openETCS project
\item Whoever is a newcomer to the project, has to be able to go through the
 QA Plan and has to get an idea what is the right behaviour in openETCS
 project.
\end{enumerate}
 
We still have to figure out which additional Documents are needed to achive
 our ideas 1 and 2.
 We also agreed that every document has to have a it's fix owner.

 We came to the conclusion that a team is needed to take care of certain
 parts of the QA Plan and related documents.
 We further agreed that the team will work with SCRUM strategy.
 
Since we are in an Open Source enviroment, we need a bunch of volunteers
 who would like to contribute to the QA Plan development.
 Following partners have already announced their participation:\\
 Jan Welte\\
 Merlin Pokam\\
 Cyril Cornu\\
 Bernd Hekele\\
 Rico Kaseroni as the owner of the Document
 
Further I have to discuss with Uwe Steinke and Fausto Cochetti on their
 possible contribution.
 Whoever else who is interested to contribute to the QA Plan development, is
 more than welcome to discuss her/his contribution with the team above.
 


\line(1,0){400}
\section*{\underline{Notes}}

\end{document}
