
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute open ETCS}
\author{Hekele, Bernd}
\date{2013-02-15}

\begin{document}
\section*{\large{Meeting Minute open ETCS \ \ \ \ 2013-02-15}}

\large{\emph{Called up by: \ \  Dr. Klaus Ruediger Hase.}}

\subsection*{Participants:} 
WP5, Klaus-Ruediger Hase, Fausto Cocchetti, Jan Welte,  Marc Behrens, Merlin Pokam, Joao Santos, Rico Kaseroni

\subsection*{Meeting Time: from 09:30h \ to: \ 10:00h}

\subsection*{Type of conference: Telco}

\line(1,0){400}
\section*{\underline{Agenda}}
\begin{enumerate}
\item Intermediate Report to DLR
\item Formal Tools Workshop
\item Update on TCSim status
\end{enumerate}
\line(1,0){400}
\section*{\underline{Discussion}}

\begin{enumerate}

\item Report is due today, i.e., Friday, 15th February.\newline
If report cannot be sent in time the delay has to be announced to Holger Stegemann (TO) and Yvonne Loehel (CC), both at dlr.de.\newline
Please, send a copy of the report (resp. the delay announcement) to project-office. The copy is also needed to prepare the German cluster summary report and the project report to ITEA. 
For ITEA reporting a English version of the report is highly appreciated.

\item Formal Tools workshop\newline
Regarding schedule the best match for most of the participants is week beginning 15th of April. 

\item Update on TCSim status\newline
DB Netz plans to take the train simulator TCSim into the project. First restoration steps are started. Part of WP5 is the use of TCSim as a demonstrator. Activities for this task have to be planned in cooperation with DB Netz, ERSA and Krauss Maffei Wegmann.

\end{enumerate}

\line(1,0){400}
\section*{\underline{Notes}}

\end{document}
