
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}



% Page layout (geometry)
\title{Meeting Minute open ETCS}
\author{Hekele, Bernd}
\date{2013-03-06}

\begin{document}
\section*{\large{Meeting Minute open ETCS \ \ \ \ 2013-03-01}}

\large{\emph{Called up by: \ \  Dr. Klaus-Ruediger Hase.}}

\subsection*{Participants:} PMB, Klaus-Ruediger Hase, Marc Behrens, Baseliyos Jacob, Michael Jastram, Pierre-Francois Jauquet, Jan Welte\\

\subsection*{Meeting Time: from 11:00h \ to: \ 11:30h}

\subsection*{Type of conference: Telco}

\line(1,0){400}
\section*{\underline{Agenda}}
\begin{enumerate}
\item ITEA 2 effort plan to be updated: outstanding deliveries
\item ITEA 2 Project Report: contributions
\item "API Requirements" Workshop and "Sefety Requirements" Workshop
\item Project Proposals for decision
\item Bringing Scrum into Locations
\item Agile Backlog Tool "Greenhopper \& Jira for openETCS

\end{enumerate}
\line(1,0){400}
\section*{\underline{Discussion}}

\begin{enumerate}

\item ITEA2 effort plan to be updated: outstanding deliveries\newline
There are stil a couple of efforts updates in the ITEA DB not confirmed / updated.

\item ITEA2 Project Report: contributions
Your contribution is required for compiling the ITEA2 Project Report. Peter Mahlmann will collect your input.

\item "API Requirements" Workshop and "Sefety Requirements" Workshop
For details see minutes of WP4 scrum meeting

\item Project Proposals for decision:\newline
The following  project proposals have been discussed and excepted:
\begin{enumerate}
\item WP4: vv Report

\item WP3b: Model Evaluation

\item WP7: Eclipse Platform Evaluation

\item WP4: Internal Assessor

\item WP4: Identification Of Tools And Profile Usage

\item WP2: CENELEC compliance report
\end{enumerate}

Repositories will be implemented as soon as possible (public).\newline
The following proposal is still pending. Some questions regarding the usecase of the task could not be closed during the meeting:

\begin{enumerate}
\item WP3a: ERTMSFormalSpecs Project proposal
\end{enumerate}

\item Bringing Scrum into Locations
\item Agile Backlog Tool "Greenhopper \& Jira for openETCS
The tool is available for use in openETCS. Interested parties are asked to call Bernd Hekele. A introduction strategy is planned to be presented in next PMB.
\end{enumerate}

\line(1,0){400}
\section*{\underline{Notes}}

\end{document}
